A Case Study in Preserving a High Energy Physics Application

### 2014-01-28 paper.tex
add Coarse-Grained Method

>>>>

Understanding all the remote and local dependencies of one program, one self-contained package can be built from scratch by copying all the dependencies directly using coarse-grained method,
which means copying the whole local filesystem, HDFS, PanFS, together with each complete remote repository without selection, into the new package.
However, the whole OS and local filesystem do not exist only for this special program, and contain a lot of files and software unrelevant to this special program. 
The size of HDFS, PanFS, remote CMSSW repository all reaches TB level. 
This solution is easy to implement, but time-consuming and space-consuming.
Through observation, we noticed that the size of really used data and software is greatly less than the original total size. 
Therefore, one fine-grained toolkit generating the target package is necessary.
